Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-10-22 manuscript/manuscript.Rmd
Adding to the Methods section.

A few paragraphs about the context of what has been done with conjoint analysis within the political and/or public policy field.

>>>>

Conjoint analysis has been widely used within social sciences but has only recently been used in the political and public policy field. Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess tradeoffs made in political communications. Conjoint is key in political research because helps it captures multidimensional causal relations.

Knudsen and Johannesson (2018) showed that political communication requires conjoint analysis because __________.

"Conjoint addresses [the issues of the traditional survey] by separately identifying several component-specific causal effects." (pg. 11)
